\documentclass[
%12pt,a4paper
fromphone,fromemail,fromalign=right,
backaddress=false,
foldmarks=false,
]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{url}

\begin{document}

%\title{Cover letter}


\setkomavar{fromname}{Aleix Llusà Serra}
\setkomavar{fromaddress}{
  Department of Electronic System Design and Programming (DiPSE)\\
  Universitat Politècnica de Catalunya\\
  Av.~Bases de Manresa 61--73\\
  08242 Manresa, ES-CT
}
\setkomavar{fromphone}{+34 938777317}
\setkomavar{fromemail}{aleix@dipse.upc.edu}
% \setkomavar{signature}{Aleix Llusà Serra, Sebastià Vila-Marta, and Teresa Escobet Canal}
% \renewcommand*{\raggedsignature}{\raggedright}

\newcommand\Sigline[4][t]{%
  \parbox[#1]{.333\linewidth}{\raggedright#2}%
  \parbox[#1]{.333\linewidth}{\raggedright#3}%
  \parbox[#1]{.333\linewidth}{\raggedright#4}%
}
\setkomavar{signature}{% 
   \Sigline{Aleix Llusà Serra}{Sebastià Vila-Marta}{Teresa Escobet Canal} \\
%   \Sigline{Doctoral student}{Position 2}{Position 3} \\
}



 \begin{letter}{Editorial Board of Information Systems}


   \opening{Dear editor,}

We are submitting a manuscript entitled \emph{A new Multiresolution Time
Series Database Formal Model} for consideration of publication in
\emph{Information Systems}. It has not been published elsewhere and it has
not been submitted simultaneously for publication elsewhere.  All
authors have seen and approved the manuscript and have contributed
significantly for the paper.

This paper aims to describe a database model that manages
multiresolution time series data. Multiresolution compresses time
series with different resolutions and attribute aggregation functions.
The model is targeted to time series systems that do not need to store
all data but a summary of information is sufficient.  This model is one
of the main results from a PhD Thesis conducted during last three
years about soon to be completed. This research has been supported by
predoctoral grant and Spanish research projects.


Regarding experimentation purposes, we have implemented our model with
Python programming language and tested it successfully with real sensor
data coming from \emph{i-Sense}, which is an UE project.



   We hope that it will interest your audience.

   \closing{Best Regards,}

 \end{letter}

\end{document}
