\documentclass[twocolumn,11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{amsmath,amssymb}

%
% DO NOT CHANGE THE FOLLOWING PART
%
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.5in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0pt}
\setlength{\topmargin}{-0.25in}
\setlength{\columnsep}{0.4in}
\setlength{\parindent}{4ex}
%
\newtheorem{definition}{Definition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
%
%
% THIS IS THE PLACE FOR YOUR OWN DEFINITIONS
%
\newcommand{\R}{\mathbb{R}} % the set of real numbers
%
\DeclareMathOperator*{\nex}{next}
\DeclareMathOperator*{\prev}{prev}
\newcommand{\acro}[1]{\textsc{\lowercase{#1}}}


\usepackage{tikz,pgfplots}
\usetikzlibrary{dateplot}
\usetikzlibrary{shapes,arrows,positioning}
\input{imatges/estils_pgf.tex}

\usepackage[
style=numeric-comp,
sortcites=true,
% backref=true,
]{biblatex}
\bibliography{bibliografia}
\ExecuteBibliographyOptions{
  isbn=false,url=false,doi=false,eprint=false,alldates=terse,firstinits=true,abbreviate=true,maxnames=2,
}
\bibitemsep 0mm \bibnamesep 0mm \bibinitsep 0mm \biblabelsep 1mm \bibhang 0mm 



\input{wseas_latex}

\usepackage[bookmarks,pdfborder={0 0 0}]{hyperref}

\hypersetup{
    pdftitle={A Model for a Multiresolution Time Series Database
  System},
    pdfauthor={Aleix Llusà Serra; Teresa Escobet Canal, Sebastià Vila Marta},
    pdfcreator={DiPSE--UPC},
    pdfsubject={AIKED13},
    pdfkeywords={time series; data model; database systems; monitoring systems},
    pdflang=en,
}


%
%
% THE BEGINNING OF THE DOCUMENT
%
\begin{document}
\global\def\refname{{\normalsize \it References:}}
%
\baselineskip 12.5pt
%
%
% TITLE, AUTHOR, ABSTRACT, KEYWORDS
%
\title{\LARGE \bf A Model for a Multiresolution Time Series Database
  System}

\date{}

\author{\hspace*{-10pt}
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{\scshape A.~LLUSÀ-SERRA}
  \end{minipage} \kern 0in
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{\scshape T.~ESCOBET-CANAL}
  \end{minipage} \kern 0in
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{\scshape S.~VILA-MARTA}
  \end{minipage} \\ \hspace*{-10pt}
  % 
  \begin{minipage}[t]{2.7in} \normalsize \baselineskip 12.5pt
    \centerline{Universitat Politècnica de Catalunya}
    \centerline{Department of Electronic Systems Design and Programming}
    \centerline{Av.~Bases de Manresa 61--73, 08242 Manresa}
    \centerline{\scshape ES-CT}
  \end{minipage}
  \\[14pt]
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{aleix@dipse.upc.edu}
  \end{minipage} \kern 0in
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{teresa.escobet@upc.edu}
  \end{minipage} \kern 0in
  \begin{minipage}[t]{2.3in} \normalsize \baselineskip 12.5pt
    \centerline{sebas@dipse.upc.edu}
  \end{minipage} 
  % % 
  % If you are three authors then you can use three mini--pages
  % instead of two. Their horizontal size must be less than 2.7in
  % indicated above. It can be e.g. 2.3in. However, you must pay
  % attention that you do not exceed the total width of the text.
  % 
  \\[5pt]
  \begin{minipage}[b]{6.9in} \normalsize
    \baselineskip 12.5pt {\it Abstract:}
    % The text of the abstract follows.
    In this paper we propose a model for multiresolution time series
    database management systems. This model stores compactly a time series
    and manages consistently its temporal dimension. This is achieved by
    extracting different resolutions and attributes summaries from the
    original time series.
    % 
    Our work is concerned in putting together two areas of study: time
    series analysis and database management systems. Time series analysis
    offers a great deal of methodologies and algorithms to process time
    series data. Database systems field provides software expertise in
    managing data. Therefore, for many applications it is of primary
    relevance that database systems support time series.
    % 
    \\[4mm] \textit{Key--Words:}
    % The key-words follow.
    time series, data model, database systems, monitoring systems.
  \end{minipage}
  \vspace{-10pt}
}

\maketitle

\thispagestyle{empty} \pagestyle{empty}
% numbers of pages are supplemented by the editor
%
% THE BEGINNING OF THE TEXT
%

%intro, requirements
\input{intro-wseas}

%model MTSMS
\input{model-wseas}

%exemple
\input{example-wseas}

%related work, conclusion, acknowledgement
\input{conclusion-wseas}

\vspace{5pt plus 5pt} 
\noindent \textbf{Acknowledgements:} The research presented in this
paper has been supported by Spanish research project \textsc{nasp
  (TEC2012-35571)}, \textsc{sherecs (dpi2011-26243)}, the UE project
i-Sense ({\small FP7-ICT-270428}), and Universitat Polit\`{e}cnica de
Catalunya.


\pdfbookmark{References}{bookmark:references}
\printbibliography{}
\end{document}



%%% Local Variables:
%%% ispell-local-dictionary: "british"
%%% End: