\documentclass{scrartcl}
\usepackage[utf8]{inputenc}

\usepackage{todonotes}

\usepackage{url}

\usepackage[hmargin=2cm,vmargin=4cm,columnsep=7.5mm]{geometry}

\usepackage{biblatex}
\bibliography{bibliografia}

\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

\usepackage{tikz}
\usepackage{multicol}
\usepackage{graphicx}
\newcommand{\imatges}{../../imatges}
\newcommand{\experiment}{../../../src/experiments/trunk}


\newtheorem{definition}{Definition}
\DeclareMathOperator*{\nex}{next}
\DeclareMathOperator*{\prev}{prev}

\title{
  Model and requirements for a Multiresolution Time Series
  Database Management System }


%[A. Llusà Serra; T. Escobet Canal, S. Vila-Marta]
\author
{
  {
    A.\ Llusà Serra,
    T.\ Escobet Canal
    and S.\ Vila-Marta
  }\\
  {\{aleix,sebas\}@dipse.upc.edu, teresa.escobet@upc.edu}\\
  {Department of Electronic System Design and Programming (DiPSE)}\\
  {Universitat Politècnica de Catalunya, 08242 Manresa, Spain}
}



\begin{document}


\maketitle


\begin{abstract}
The abstract goes here.
Manuscripts should be written in English and include a 100-300 word abstract.

Tot i que el el món d'analàsis de sèries temporals trobem multitud de metodologies i algoritmes per analitzar les sèries temporals, no hi ha suport en els SGBD per a gestionar-ho.
\end{abstract}

{\bfseries Keywords:} 




%\twocolumn



\section{Introduction}



Modern society depends on the smooth operation of many complex
engineering systems which provides products and services. Examples
include electric power systems, water distributions networks,
transportation systems, manufacturing processes, intelligent
buildings, communication systems, etc. The emergence of networked
embedded systems and sensor/actuator networks has made possible the
collection of large amounts of real-time data for monitoring and
control of such complex systems.  In most application, these data need
to be processed and synthesized efficiently to provide relevant
information to engineers, researchers, accident investigators,
operators, and many other users. Nevertheless, before using the
collected signals, it is of primary importance to promptly detecting
eventual sensor failures or malfunctions and possibly reconstructing
the incorrect signals in order to avoid processing misleading
information which may lead to unsafe and/or inefficient actions. The
correctness of those real-time data depends not only on the measured
value, but also on the time as it is collected. When observations are
collected at frequent time interval, large data sets in the form of
time series are generated
(http://www.springerlink.com/content/442wp9xq56286245/fulltext.pdf). In
(http://www.sciencedirect.com/science/article/pii/S0952197610001727) a
time series is defined as a collection of observations made
chronologically, in \cite{last:hetland} they are also called time
sequences.  The procedure of processing and synthesizing information
becomes complicated if the behavior of the series varies over time.
The research in time series data mining has increased last decade and
the key to success is reducing the dimension of time series in order
to be able process the data in a reasonable time.

Time series are usually stored in a database.     i a partir d'aqui introduir el que és el Data Based Managment System .....






This paper focuses on Data Base Management Systems (DBMS) that store
and treat data as time series, known as Time Series Data Base
Management Systems (TSMS). Traditional DBMS, as is ones derived from
relational model, are not adequate for these cases as they do not have
enough facilities to manage and retrieve time series information.

Although there is no standard model for TSMS, there are some interesting proposals \cite{dreyer94,zhang11}. We will define a multiresolution TSMS (MTSMS) as being a TSMS defining the basic concepts where needed.





Unió entre els dos camps d'anàlisis de sèries temporals i de models de SGBD. 

- Multitud d'algoritmes i metodologies. Problemes en el monitoratge.
- Model relacional és referent




Motivació: vam observar RRDtool [citar tfm?] i volíem entendre els conceptes i modelar-los per tal de veure'n la flexibilitat: RRDtool és molt restringit amb el tractament amb el temps i amb el tipus de dades que pot tractar.



** Paper structure **



\section{Requirements for a MTSMS}

A TSMS is a special purpose DBMS aimed at storing and managing time
series and MTSMS is a TSMS with multiresolution capabilities. Next we
describe the main requirements that a TSMS must achieve, specifically
remarking the improvements where the MTSMS can contribute.



* Alta dimensió sèries temporals, cal reduir-la. Es conserven els segments de temps més interessants; multiresolució


* Multiresolució, diferents resolucions, es pot treballar amb més o menys dades segons convingui

* Cal saber canviar de resolució, exemple transformar dades periòdiques d'un mes a un any.

* Visualització adequada de les sèries temporals: no cal emmagatzemar resolucions i informacions sinó es volen mostrar


* Temporal databases. Basades en esdeveniments. Data mining basat en sèries temporals definides per parelles temps-valor; calen TSMS [schmidt i dreyer] 



* Cal censurar les dades.

* Cal regularitzar les sèries temporals, o saber operar amb elles quan no són regulars. La no regularitat en el temps de mostreig pot provenir per exemple de jitter en mostrejos periòdics (problemes estudiats en el control) o d'un event-based sampling/control.


* Aggregates, una sèrie temporal pot estar mostrant diferent informació. ex: mitjana, màxim, valor al final del període, ...

* Les sèries temmporals tenen una metainformació que cal guardar en una base de dades relacional (localització, etiquetes de classificació, últim valor mesurat, unitats, etc.) [dreyer]



* Calendari, passa a segon terme, (en contraposició a Dreyer). El temps es defineix com universal i constant (semblant a Unix Time Epoch). Aquests temps es pot convertir a calendari. Cal definir la interacció usuari/calendari amb temps universal.

* El temps és un nom donat al camp, qualsevol objecte que tingui la mateixa interfície que el temps pot funcionar. En el cas del valor pot ser qualsevol objecte, s'exemplifica amb reals per facilitar-ne la comprensió i per ser el més proper al time series analysis: statistical methods focused on sequences of values representing a single numeric variable [llibre-last].




* Representació: Entre dos punts de mesura, quin valor pren la sèrie temporal?.


* Disseny del model de TSMS, aleshores veurem si una TSMS pot ser implementada com a camp d'una altra DBMS o si els DBMS no són capaços de manipular TS adequadament i cal implementar TSMS específics.

* Xarxa de sensors, tsms distribuïda. Sensor dades recents, màquina grossa històrics. Quan es llança una consulta, es llança distribuïdament: si es té prou resolució es respon sinó s'envia la consulta al sensor. [bonnet01?]

* S'ha de poder calcular incrementalment, citar data streams


\section{The multiresolution model}

\input{model}


%exemple
\input{example}




\section{Related Work}


\todo{una mica d'intro}: L'objectiu de dissenyar SGBD per a sèries temporals gaudeix d'un gran interès actualment.

On the one hand, there are DBMS with some properties and operations
for time series.

RRDtool from Oetiker \cite{rrdtool} is a professional database
management system extremely used by the free software community. It is
used in professional monitoring systems and its efficiency and speed
when processing time series is being improved. Nevertheless, it is
focused to a particular kind of data, gauges and counters, and it has
not general time series operations.

Cougar \cite{bonnet01} is a sensor database system. It has two
structures: one for sensor properties stored into relations and
another for time series stored into data sequences from sensors.  Time
series have specific operations and can combine relations and
sequences.


SciDB \cite{stonebraker09:scidb} and SciQL \cite{zhang11} are array
database systems. These systems are intended for science applications,
in which time series play a principal role. They structure time series
into arrays in order to achieve multidimensional analysis.



On the other hand, the relational DBMS model is continuously evolving
\todo{citar third manifesto?}. Particularly regarding time data,
intensive research has been carried in the bitemporal data field, that
is the management of history using time intervals.  The recent
temporal data research in relational DBMS model terms
\cite{date02:_tempor_data_relat_model} marks a promising
foundation. It models bitemporal data as relations extended with time
intervals attributes and extends relational operations in order to
deal with related time aspects.

Although bitemporal data and time series data are not exactly the same
and so can not be treated interchangeably \todo{cita, schidmidt95?},
time series research can benefit from two aspects of this bitemporal
data research. First, it shows the way to extend relational DBMS with
new types and how to model them. Second, it settles some time-related
concepts that can apply well to time series.






\section{Conclusions and future work} 
The conclusion goes here.

Hem vist un model de MTSMS, quins requeriments tenen aquests sistemes i com es podria aplicar en un exemple. L'objectiu és emmagatzemar les sèries temporals de forma compacta i gestionar-les amb coherència amb la dimensió temporal. 

Hem vist el primer pas per definir el model de dades per a un MTSMS, en un futur caldrà definir-ne les operacions i un model de dades que agrupi propietats generals dels TSMS com poden ser la unió de sèries temporals, el càlcul d'itervals temporals, etc.

Amb aquesta recerca volem demostrar que l'ús de SGBD per a les sèries temporals facilitarà enormement el treball amb aquestes.
L'interès actual ens fa ser optimistes per aventurar que aviat podrem gestionar les sèries temporals adequadament amb els SGBD.



\section*{Acknowledgements}

This work was supported by Universitat Polit\`{e}cnica de Catalunya (UPC).

Data comes from iSense project \todo{isense}.

\printbibliography{}
% \bibliographystyle{plain}
% \begin{thebibliography}{99}


% \bibitem{llusa11:tfm} A.\ Llusà Serra, ``Estudi i modelització
%   dels SGBD Round Robin pel tractament de sèries temporals''
%   (catalan), Master Thesis, Universitat Politècnica de Catalunya,
%   2011.  \todo{no citat}

% \bibitem{llusa12:ptd} A.\ Llusà Serra, ``Disseny i modelització
%   d'un sistema de gestió multiresolució de sèries temporals''
%   (catalan), Thesis Proposal, Universitat Politècnica de Catalunya,
%   2012. \url{http://escriny.epsem.upc.edu/attachments/download/13/projecte-tesi.pdf} \todo{no citat}


% \bibitem{rrdtool} T.\ Oetiker, ``RRDtool, Round Robin database'',
%   1998--2011.  \url{http://oss.oetiker.ch/rrdtool/}

% \bibitem{lisa98:oetiker} T.\ Oetiker, ``MRTG The Multi Router Traffic Grapher``, In: Proceedings of the 12th Sys-
%      tems Administration Conference. LISA’98. Boston, Massachusetts: USENIX Association,
%      12-1998, p`gs. 141–148.
%                a



% \bibitem{fung02} W.\ Fu Fung, D.\ Sun and J.\ Gehrke, ``COUGAR: the
%   network is the database'', Proceedings of the 2002 ACM SIGMOD
%   international conference on Management of Data, Madison, 4--6 June
%   2002, pp. 621--621. doi: 10.1145/564691.564775

% \bibitem{bonnet01}

% \bibitem{stonebraker09:scidb}

% \bibitem{zhang11}

% \bibitem{ddl02}

% \bibitem{last:keogh} LATS:KEOGH

% \bibitem{last:hetland}LAST:hetland

% \bibitem{keogh01} keogh01



% \end{thebibliography}           




\end{document}




%%% Local Variables: 
%%% ispell-local-dictionary: "british"
%%% End: 