\documentclass[
%  prepint,
  review,
  twocolumn,
  5p,
  sort&compress,
]{elsarticle}

\journal{Information Systems}


\usepackage{todonotes}
\presetkeys%
{todonotes}
{inline}
{}



\usepackage{amsmath,amssymb}
\usepackage[pdfborder={0 0 0}]{hyperref}


\usepackage{listings}
\lstdefinestyle{py}{
  language=python,
  escapechar=æ,
  breaklines=true,
  %basicstyle=\ttfamily,
  showspaces=false,
  keepspaces=true,
}


\usepackage{supertabular}





\newcommand{\acro}[1]{\textsc{\lowercase{#1}}}
\newcommand{\R}{\mathbb{R}} % the set of real numbers
\newcommand{\Rb}{\bar\R} % the set of bar real numbers
\newcommand{\Rp}{\R^{*}} % the set of projectively real numbers
\newcommand{\N}{\mathbb{N}} % the set of natural
\newcommand{\zohe}{\acro{zohe}}
\newcommand{\dd}{\acro{DD}}

\DeclareMathOperator*{\inst}{\in^t}
\DeclareMathOperator*{\notinst}{\notin^t}
\DeclareMathOperator*{\subseteqt}{\subseteq^t}
\DeclareMathOperator*{\cupt}{\cup^t}
\DeclareMathOperator*{\dift}{-^t}
\DeclareMathOperator*{\join}{JOIN}
\DeclareMathOperator*{\map}{map}
\DeclareMathOperator*{\fold}{fold}
\DeclareMathOperator*{\agg}{aggregate}
\DeclareMathOperator*{\fmap}{f}
\DeclareMathOperator*{\ffold}{g}
\DeclareMathOperator*{\fagg}{g}
%\DeclareMathOperator*{\orderfold}{ofold}
\DeclareMathOperator*{\nex}{next}
\DeclareMathOperator*{\prev}{prev}
\DeclareMathOperator*{\graph}{graph}

\DeclareMathOperator{\addB}{addB}
\DeclareMathOperator{\consB}{consB}
\DeclareMathOperator{\addD}{addD}
\DeclareMathOperator{\addR}{addR}
\DeclareMathOperator{\consR}{consR}
\DeclareMathOperator{\addM}{addM}
\DeclareMathOperator{\consM}{consM}
\DeclareMathOperator{\seriedisc}{SerieDisc}
\DeclareMathOperator{\totalseries}{TotalSeries}

\DeclareMathOperator{\dmap}{Dmap}
\DeclareMathOperator{\multiresolution}{multiresolution}

\DeclareMathOperator{\meanz}{mean^\zohe}
\DeclareMathOperator{\maxz}{maximum^\zohe}



\bibliographystyle{elsarticle-num}




\begin{document}



%%PARAMETRES
\newdefinition{definition}{Definition}
\newdefinition{example}{Example}


\begin{frontmatter}

  \title{A Multiresolution Time Series \\ Database Formal Model}


  \author
  [dipse]
  {Aleix Llus\`{a} Serra\corref{mycorrespondingauthor}
  }
  \cortext[mycorrespondingauthor]{Corresponding author. Tel: +34 938777317}
  \ead{aleix@dipse.upc.edu}

  \author
  [dipse]
  {Sebasti\`{a} Vila-Marta
  }
  \ead{sebas@dipse.upc.edu}

  \author
  [dipse]
  {Teresa Escobet Canal
  }
  \ead{teresa.escobet@upc.edu}



  \address
  [dipse]
  {Department of Electronic System Design and Programming\\ Universitat Polit\`{e}cnica de Catalunya\\ Av.~Bases de Manresa 61--73, 08242 Manresa, ES-CT}



  \begin{abstract}
    In this paper we formalise a model for multiresolution time series
    database management systems. These are special purpose systems
    that store each time series lossy compressed by extracting
    different resolutions and attribute aggregations. Then time series
    are stored compactly, with finite capacity and with its temporal
    attribute managed consistently.

    
    This model is \todo{original,novel} in terms of database formalism.  It
    is a generic approach to what we call multiresolution features, as
    instance we formalise it open so that users can define any
    attribute aggregations.  Furthermore, we consider some time series
    analysis specific properties that can be problematic when
    manipulating them in the multiresolution approach.
    We use the time-order acquisition characteristic of
    time series to simplify its treatment by stream-like computations
    in order to achieve fast pre-computed queries and
    visualisations. We design RoundRobinson as a referent
    implementation of the model.



    % We root our theory firmly on set and relational algebra together
    % with some time series analysis specific properties that can be
    % problematic when manipulating them.


\todo{should appear:}
* Our \acro{MTSMS} model is a generic approach to the multiresolution
features, we formalise it open so that users can define any attribute
aggregate functions.

* No similar work in this terms of formalism

*Implmenentation named RoundRobinson

  \end{abstract}


  \begin{keyword}
    Time series \sep database systems \sep multiresolution \sep lossy
    compression \sep approximate queries
  \end{keyword}

\end{frontmatter}


\input{intro}

\input{model}

\input{implementation}

\input{example}

\input{conclusions}



\section*{Acknowledgements}

The research presented in this paper has been supported by Spanish
research projects \textsc{tec2012-35571} and \textsc{dpi2011-26243},
the UE project i-Sense (\textsc{fp7-ict-270428}), and Universitat
Polit\`{e}cnica de Catalunya predoctoral grant.



%\section*{References}
\bibliography{bibelsarticle}




\end{document}





%%% Local Variables: 
%%% ispell-local-dictionary: "british"
%%% End: 