

\documentclass[
%  prepint,
  review,
  twocolumn,
  5p,
]{elsarticle}

\journal{Information Systems}


\usepackage{amsmath,amssymb}
\usepackage[pdfborder={0 0 0}]{hyperref}


% \usepackage{todonotes}
% \presetkeys%
% {todonotes}
% {inline}
% {}


\usepackage{tikz,pgfplots}
\usetikzlibrary{dateplot}
\usetikzlibrary{shapes,arrows,positioning}
\input{imatges/estils_pgf.tex}
\usepackage{imatges/tikz-uml}

\usepackage{listings}
\lstdefinestyle{py}{
  language=python,
  escapechar=æ,
  breaklines=true,
  %basicstyle=\ttfamily,
  showspaces=false,
  keepspaces=true,
}


\usepackage[
%          counter=section,
%          acronym,
          nonumberlist,
          %%toc,
          nomain,
%          section,
%          numberedsection=autolabel,
%          sanitize=none, %pels accents en el vegeu
          ]{glossaries}




\newglossary{notation}{not}{ntn}{Notation symbols}
\newglossarystyle{estil-notation}{%
  \renewcommand{\glsgroupskip}{}% make nothing happen between groups
  \renewenvironment{theglossary}
  {\begin{supertabular}{ll}}{\end{supertabular}}
  \renewcommand*{\glossarysubentryfield}[6]{%
    \Glsentryname{##2} & ##4  \\
    %\Glsentryname{##2}
    %\glstarget{##2}{##3}% the entry name
%    \item \glstarget{##2}{\Glsentryname{##2}}% the entry name
    % &
    %  %\space (##5)% the symbol in brackets
    % \space ##4% the description
    % &
    % \space [##6]% the number list in square brackets
    % \\                                    
  }%
  \renewcommand*{\glossaryentryfield}[5]{%   
    %\glossarysubentryfield{##2}{##1}{##2}{##3}{##4}{##5}
    \bf{\Gls{##1}}  & ##3 \\
  }
}


\glsdisablehyper
\makeglossaries
\loadglsentries[notation]{notation_table.tex}





\newcommand{\acro}[1]{\textsc{\lowercase{#1}}}
\newcommand{\R}{\mathbb{R}} % the set of real numbers
\newcommand{\Rb}{\bar\R} % the set of bar real numbers
\newcommand{\N}{\mathbb{N}} % the set of natural
\newcommand{\zohe}{\acro{zohe}}

\DeclareMathOperator*{\inst}{\in^t}
\DeclareMathOperator*{\notinst}{\notin^t}
\DeclareMathOperator*{\subseteqt}{\subseteq^t}
\DeclareMathOperator*{\cupt}{\cup^t}
\DeclareMathOperator*{\dift}{-^t}
\DeclareMathOperator*{\join}{join}
\DeclareMathOperator*{\map}{map}
\DeclareMathOperator*{\fold}{fold}
\DeclareMathOperator*{\agg}{aggregate}
\DeclareMathOperator*{\orderfold}{ofold}
\DeclareMathOperator*{\nex}{next}
\DeclareMathOperator*{\prev}{prev}
\DeclareMathOperator*{\graph}{graph}

\DeclareMathOperator{\addB}{addB}
\DeclareMathOperator{\consB}{consB}
\DeclareMathOperator{\addD}{addD}
\DeclareMathOperator{\addR}{addR}
\DeclareMathOperator{\consR}{consR}
\DeclareMathOperator{\addM}{addM}
\DeclareMathOperator{\consM}{consM}
\DeclareMathOperator{\seriedisc}{SerieDisc}
\DeclareMathOperator{\totalseries}{TotalSeries}

\DeclareMathOperator{\dmap}{Dmap}
\DeclareMathOperator{\multiresolution}{multiresolution}

\DeclareMathOperator{\meanz}{mean^\zohe}
\DeclareMathOperator{\maxz}{maximum^\zohe}



\bibliographystyle{elsarticle-num}




\begin{document}



%%PARAMETRES
\newdefinition{definition}{Definition}
\newdefinition{example}{Example}


\begin{frontmatter}

  \title{A new Multiresolution Time Series \\ Database Formal Model}

  \author
  [dipse]
  {Teresa Escobet Canal
%    \fnref{order}
}
  \ead{teresa.escobet@upc.edu}

  \author
  [dipse]
  {Aleix Llus\`{a} Serra\corref{mycorrespondingauthor}
%    \fnref{order}
  }
  \cortext[mycorrespondingauthor]{Corresponding author. Tel: +34 938777317}
  \ead{aleix@dipse.upc.edu}

  \author
  [dipse]
  {Sebasti\`{a} Vila-Marta
%    \fnref{order}
  }
  \ead{sebas@dipse.upc.edu}

  \address
  [dipse]
  {Department of Electronic System Design and Programming\\ Universitat Polit\`{e}cnica de Catalunya\\ Av.~Bases de Manresa 61--73, 08242 Manresa, ES-CT}

 
%  \fntext[order]{The authors are listed as per alphabetical order.}


  \begin{abstract}
    In this paper we define a model for multiresolution time series
    database management systems. These systems store each time series
    lossy compressed by extracting different resolutions and attribute
    aggregations. Then time series are stored compactly, with finite
    capacity and with its temporal attribute managed consistently.

    For many applications it is of primary relevance that database
    systems support time series.  We root our theory firmly on set and
    relational algebra together with some time series analysis
    specific properties that can be problematic when manipulating
    them.  Furthermore, we use the time-order acquisition
    characteristic of time series to simplify its treatment by
    stream-like computations in order to achieve fast pre-computed
    queries and visualisations.
  \end{abstract}

  % % A category with the (minimum) three required fields
% \category{H.2}{Information Systems}{Data Management Systems}[Database design and models]
% %A category including the fourth, optional field follows...
% %\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

% \terms{Theory}

  \begin{keyword}
    Time series \sep database systems \sep multiresolution \sep lossy
    compression \sep approximate queries
  \end{keyword}

\end{frontmatter}


\input{intro}

\input{model}

\input{implementation}

\input{example}

\input{conclusions}




\section*{Acknowledgements}
%\todo{incorrectes: T envia les noves}

The research presented in this paper has been supported by Spanish
research projects \textsc{tec2012-35571} and \textsc{dpi2011-26243},
the UE project i-Sense (\textsc{fp7-ict-270428}), and Universitat
Polit\`{e}cnica de Catalunya predoctoral grant.



\section*{References}
\bibliography{bibelsarticle}


\glsaddall
\appendix
\section{Notation}
\label{sec:notation}


{\small
Name and symbol notation. Divided into
\acro{TSMS} and \acro{MTSMS} notation and each organised into its
components.
\setglossarysection{paragraph}
\printglossary[type=notation,style=estil-notation,title=]
}



\end{document}





%%% Local Variables: 
%%% ispell-local-dictionary: "british"
%%% End: 