\section{Conclusion} 
\label{sec:concl-future-work}

In this paper we have shown a \acro{MTSMS} model, including the
requirements for these special systems and how they can be applied to
an example time series. The main objective is to store compactly a
time series and manage consistently its temporal dimension.

Our \acro{MTSMS} model proposes to store a time series split into time
subseries, which we call resolution discs.  Each resolution disc has a
different resolution and is compacted with an attribute aggregate
function. Therefore, in a multiresolution database the configuration
parameters are the quantity of resolution discs and each of their
three parameters: the consolidation step, the attribute aggregate
function and the capacity.

The data model shown is the first step to develop a complete model for
a \acro{MTSMS}. In the future the operations will be defined. In this
context, there is a need for a model collecting generic properties for
the \acro{TSMS}, as it can be the time series union operation or the
time interval operations. Then, the multiresolution model would be
build upon the generic \acro{TSMS} model.

Concluding, in this paper we show that using \acro{TSMS} facilitates
substantially time series management. The current field interest makes
us optimistic to expect soon an adequate management in \acro{DBMS}.

%%% Local Variables:
%%% TeX-master: "main-wseas"
%%% ispell-local-dictionary: "british"
%%% End:

% LocalWords: multiresolution MTSMS DBMS RDBMS TSMS
