\documentclass[
  preprint,
  review,
  twocolumn,
  5p,
  sort&compress,
]{elsarticle}

\journal{Information Systems}




\usepackage{amsmath,amssymb}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{url}





\newcommand{\acro}[1]{\textsc{\lowercase{#1}}}
\newcommand{\R}{\mathbb{R}} % the set of real numbers
\newcommand{\Rb}{\bar\R} % the set of bar real numbers
\newcommand{\Rp}{\R^{*}} % the set of projectively real numbers
\newcommand{\N}{\mathbb{N}} % the set of natural
\newcommand{\zohe}{\acro{zohe}}
\newcommand{\dd}{\acro{DD}}
\newcommand{\join}{\ensuremath{\Join}}


\DeclareMathOperator*{\inst}{\in^t}
\DeclareMathOperator*{\notinst}{\notin^t}
\DeclareMathOperator*{\subseteqt}{\subseteq^t}
\DeclareMathOperator*{\cupt}{\cup^t}
\DeclareMathOperator*{\dift}{-^t}
\DeclareMathOperator*{\map}{map}
\DeclareMathOperator*{\fold}{fold}
\DeclareMathOperator*{\agg}{aggregate}
\DeclareMathOperator*{\fmap}{f}
\DeclareMathOperator*{\ffold}{g}
\DeclareMathOperator*{\fagg}{g}
%\DeclareMathOperator*{\orderfold}{ofold}
\DeclareMathOperator*{\nex}{next}
\DeclareMathOperator*{\prev}{prev}
\DeclareMathOperator*{\graph}{graph}

\DeclareMathOperator{\addB}{addB}
\DeclareMathOperator{\consB}{consB}
\DeclareMathOperator{\addD}{addD}
\DeclareMathOperator{\addR}{addR}
\DeclareMathOperator{\consR}{consR}
\DeclareMathOperator{\addM}{addM}
\DeclareMathOperator{\consM}{consM}
\DeclareMathOperator{\seriedisc}{SerieDisc}
\DeclareMathOperator{\totalseries}{TotalSeries}

\DeclareMathOperator{\dmap}{Dmap}
\DeclareMathOperator{\multiresolution}{multiresolution}

\DeclareMathOperator{\meanz}{mean^\zohe}
\DeclareMathOperator{\maxz}{maximum^\zohe}
\DeclareMathOperator{\dom}{dom}



\bibliographystyle{elsarticle-num}




\begin{document}



%%PARAMETRES
\newdefinition{definition}{Definition}
\newdefinition{example}{Example}


\begin{frontmatter}

  \title{Formalism for a Multiresolution Time Series Database Model}


  \author
  [dipse]
  {Aleix Llus\`{a} Serra\corref{mycorrespondingauthor}}
  \cortext[mycorrespondingauthor]{Corresponding author}
  \ead{aleix@dipse.upc.edu}

  \author
  [dipse]
  {Sebasti\`{a} Vila-Marta
  }
  \ead{sebastia.vila@upc.edu}

  \author
  [dipse]
  {Teresa Escobet Canal
  }
  \ead{teresa.escobet@upc.edu}



  \address
  [dipse]
  {Department of Electronic System Design and Programming\\ Universitat Polit\`{e}cnica de Catalunya\\ Av.~Bases de Manresa 61--73, 08242 Manresa, ES-CT}



  \begin{abstract}
    We formalise a model for multiresolution time series
    database management systems.
    %
    These special purpose database systems store time series lossy
    compressed in a space-bounded storage.
    %
    Time series can be stored at multiple resolutions, using
    distinct attribute aggregations, while keeping its temporal
    attribute consistently managed.
   
    The model exhibits a generic approach. This allows the user to
    customise it according to the actual requirements of a given
    context.
    %
    All the model pieces that hold a semantic meaning depend on
    the actual application.

    %
    Furthermore, we consider some specific time series properties that
    are a challenge in the multiresolution approach.
    %
    We also describe a reference implementation of the model
    and introduce an use case based on real data.
  \end{abstract}


  \begin{keyword}
    Time series \sep database systems \sep multiresolution \sep lossy
    compression \sep approximate queries
  \end{keyword}

\end{frontmatter}


\input{intro}

\input{model}

\input{implementation}

\input{example}

\input{conclusions}



\section*{Acknowledgements}

We would like to thank the anonymous reviewers.

The research presented in this paper has been supported by Spanish
research projects \textsc{tec2012-35571} and \textsc{dpi2014-58104-r},
and Universitat Polit\`{e}cnica de Catalunya predoctoral grant.



\section*{References}
\bibliography{bibelsarticle}




\end{document}





%%% Local Variables: 
%%% ispell-local-dictionary: "british"
%%% End: 