\newglossary{notation}{not}{ntn}{Notació}
\newglossarystyle{estil-notation}{%
  \renewcommand{\glsgroupskip}{}% make nothing happen between groups
  \renewenvironment{theglossary}
  {\begin{longtable}{ll}
      % \caption{Notació dels SGSTM \label{tab:sgstm-simbols}}
      % \endfirsthead
      % \caption[]{Notació dels SGSTM (continuació)}
      % \endhead
          % \endfoot
          % \endlastfoot
    }{\end{longtable}}
  \renewcommand*{\glossarysubentryfield}[6]{%
    \glstarget{##2}{##3}% the entry name
    &
    % \space (##4)% the symbol in brackets
    \space ##4% the description
    % \space [##6]% the number list in square brackets
    \\
  }%
  \renewcommand*{\glossaryentryfield}[5]{%
    \\\pagebreak[3]\hline
    \glossarysubentryfield{##2}{##1}{##2}{##3}{##4}{##5}
    \hline
  }
}


\renewcommand{\seename}{vegeu}
\renewcommand{\entryname}{Notació}
\renewcommand{\descriptionname}{Descripció}

\makeglossaries


%\renewcommand{\glossarypreamble}{Text com a préambul}



%TERMES


%\newglossaryentry{DBMS}{ description = {Data Base Management System} }


\newglossaryentry{domain}{ description = {sets over which relations are defined. It is the same as type} }
\newglossaryentry{type}{ description = {}, see=domain }
\newglossaryentry{SGBD-model}{ description = {Un model és}, name={Model de SGBD} }


\newglossaryentry{SBDR-cap}{ description = {La capçalera d'un SGBDR}, name={Capçalera}, parent={SGBD-model} }



\newglossaryentry{heading}{ description = {Equivalent to intension and relation schema} }
\newglossaryentry{intension}{ description = {}, see=heading }
\newglossaryentry{relation schema}{ description = {}, see=heading }

\newglossaryentry{body}{ description = {Equivalent to extension} }
\newglossaryentry{extension}{ description = {}, see=body}


\newglossaryentry{DBMS data model}{ description = {A data model (first sense) is an abstract, self-contained, logical definition of the
objects, operators, and so forth, that together constitute the abstract machine with which
users interact. The objects allow us to model the structure of data. The operators allow us
to model its behavior.\cite{date}. Sometimes it is referred as architecture.
} }

\newglossaryentry{data model}{ description = { A data model (second sense) is a model of the persistent data of some particular
enterprise. [date06]}}


\newglossaryentry{DBMS implementation}{ description = {An implementation of a given data model is a physical realization on a real
machine of the components of the abstract machine that together constitute that model.\cite{date}} }


\newglossaryentry{data independence}{ description = {model and implementation kept separated}}





\newglossaryentry{ohm}{name=ohm,symbol={\ensuremath{\Omega}},
description=unit of electrical resistance}


\newglossaryentry{relationships}{
description=relationships are semantic. relationships are entities.}


%ABREVIACIONS (abreviatures,sigles,símbols)


%ABREVIATURES



%SIGLES



%català
\newglossaryentry{SGBD}{type=\acronymtype, name={SGBD}, description={Sistema de gestió de base de dades (\emph{Data Base Management System})}, text={SGBD}, first={Sistema de gestió de base de dades (SGBD)}, plural={SGBD}, firstplural={Sistemes de gestió de bases de dades (SGBD)}}

%\newglossaryentry{SGBDR}{type=\acronymtype, name={SGBD}, description={Sistema de gestió de base de dades relacional(\emph{Relational Data Base Management System})}, text={SGBDR}, first={Sistema de gestió de base de dades (SGBD)}, plural={SGBD}, firstplural={Sistemes de gestió de bases de dades (SGBD)}}

\newacronym[first={Sistema de gestió de base de dades relacional (SGBDR)}]{SGBDR}{SGBDR}{Sistema de gestió de base de dades relacional (\emph{Relational Data Base Management System})}


%anglès
\newacronym[see=SGBD]{DBMS}{DBMS}{\nopostdesc}
\newacronym[see=SGBDR]{RDBMS}{RDBMS}{\nopostdesc}

\newacronym{MTSMS}{MTSMS}{Multiresolution Time Series Data Base management system}
\newacronym{RRDtool}{RRDtool}{Round Robin Database management system \parencite{rrdtool}}
\newacronym{SCADA}{SCADA}{Supervisory Control And Data Acquisition}
\newacronym{TSDB}{TSDB}{Time Series Data Base}
\newacronym{TSDS}{TSDS}{Time Series Data Server \parencite{weigel10}}
\newacronym{TSMS}{TSMS}{Time Series Data Base management system}
\newacronym{VLDB}{VLDB}{Very Large Data Base}



%SÍMBOLS






%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
